\documentclass[11pt]{article}

\addtolength{\topmargin}{-.8in}
\setlength{\oddsidemargin}{0.01in}
\setlength{\evensidemargin}{0.1in} \textwidth6in \textheight 10.6in
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[dvips]{graphicx}
\usepackage{nopageno}
\usepackage{amssymb}
\thispagestyle{empty}
\begin{document}

\begin{center}
\section*{STAT 946 Deep Learning}
\end{center}
\section*{Project Title: Right Whale Recognition}
\section*{Project Number: 2}

{\large \textbf{Group Members}:}\\\\
\begin{tabular}{|c|c||c| }
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Surname, First Name $~~~~~~~~$& Student ID  $~~~$  &  Your Department $~~~~~~~~$  \\
  \hline \hline
Christopher Choi & c33choi & Mechanical and Mechatronics Engineering  \\\hline
Deepak Rishi & drishi & Computer Science \\\hline
Fatemeh Karimi & f3karimi & Systems Design Engineering \\ \hline
Xinran Liu & x435liu & Systems Design Engineering \\
     \hline
\end{tabular}\\\\

	
One of our group members is taking STAT 841 (Classification)? 
\begin{itemize}
\item $\blacksquare$  No
\end{itemize}
  
Your project falls into one of the following categories. Check the
boxes which describe your project the best.

\begin{enumerate}

\item $\blacksquare$ \textbf{Kaggle project.} Our project is a Kaggle competition.
\begin{itemize} \item Our rank in the competition is 169 
\item  The best Kaggle score in this competition is 2.64, and our score is 25.8.
\end{itemize}




 \item $\Box$ \textbf{New algorithm.}  We developed a new algorithm and
 demonstrated (theoretically and/or empirically) why our technique
is better (or worse) than other algorithms. (Note: A negative result
does not lose marks, as long as  you followed proper theoretical
and/or experimental techniques). \item $\Box$ \textbf{Application.}
We applied known algorithm(s) to some domain.
\begin{itemize}
\item [$\Box$] We applied the algorithm(s) to our own research
problem.
\begin{itemize}
\item [$\Box$] We used an existing implementation of the
algorithm(s).  \item [$\Box$] We implemented the algorithm(s)
ourself.
\end{itemize}
 \item [$\Box$] We tried to reproduce results of someone
else's paper.
\begin{itemize}
\item [$\Box$] We used an existing implementation of the
algorithm(s).  \item [$\Box$] We implemented the algorithm(s)
ourself.
\end{itemize}
\end{itemize} 
\subsection*{Our most significant contributions are (List at most three):}
\begin{enumerate}
	\item{We employed Genetic Algorithm to Tune Deep Neural Architectures}
	\item{We investigated and used MLP, CNN, Autoencoders to classify whale images. Results of these methods are provided and compared.}
	\item{We tried different image pre-processing methods to extract the head patterns of Right Whale. Four datasets were generated and tested.}
\end{enumerate}

\end{enumerate}
\end{document}
